%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsectionspecifiedcolor{rainbowcolor-green}{\faBriefcase \acvHeaderIconSep Experience}
\cvsectionspecifiedcolor{awesome-red}{\faBriefcase \acvHeaderIconSep Experience}

%Adaptive – modifying the system to cope with changes in the software environment (DBMS, OS) [4]
%Perfective – implementing new or changed user requirements which concern functional enhancements to the software
%Corrective – diagnosing and fixing errors, possibly ones found by users [4]
%Preventive – increasing software maintainability or reliability to prevent problems in the future [4]


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\vspace{-0.25cm}

%---------------------------------------------------------
  \cventry
    {ASP classic Developer} % Job title
    {\href{https://www.amaris.com/}{Amaris} \textbf{(Professional)}} % Organization
    {Lisbon, Portugal} % Location
    {June 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities      
		\item[] {\textbf{Context:} adaptive, perfective and corrective banking software development. 
}
		\item[] {\textbf{Functions:} developing T-SQL queries and jobs. Adaptive, perfective and corrective banking application development.}		
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Skype/Skype for Business}, \textcolor{rainbowcolor-green}{Internet Explorer}, \textcolor{rainbowcolor-green}{MS Office Suite}, \textcolor{rainbowcolor-green}{MS SQL-Server 2005}, \textcolor{rainbowcolor-indigo}{T-SQL}, \textcolor{rainbowcolor-indigo}{ASP classic}, \textcolor{rainbowcolor-indigo}{HTML/CSS/JavaScript/XML},  \textcolor{rainbowcolor-orange}{Windows 10}.}		
      \end{cvitems}
    } 
    
%---------------------------------------------------------
  \cventry
    {Software and Oracle Database Developer} % Job title
    {} % Organization
    {} % Location
    {Jan. 2019 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities      
		\item[] {\textbf{Context:} account migration among banks, adaptive, perfective and corrective banking software development. 
}
		\item[] {\textbf{Functions:} inspecting PL-SQL queries, the sequence of queries, and then fine tuning those queries prior to sending data. Day to day support activities, investigate and address issues regarding quality of sent data with the business area. Adaptive, perfective and corrective banking software development.}		
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Redmine}, \textcolor{rainbowcolor-green}{Skype/Skype for Business}, \textcolor{rainbowcolor-green}{MS Office Suite}, \textcolor{rainbowcolor-green}{Apache AirFlow}, \textcolor{rainbowcolor-green}{Apache Ant}, \textcolor{rainbowcolor-green}{Apache Maven}, \textcolor{rainbowcolor-green}{Apache Tomcat}, \textcolor{rainbowcolor-green}{Apache Struts}, \textcolor{rainbowcolor-green}{Eclipse}, \textcolor{rainbowcolor-green}{Oracle SQL developer}, \textcolor{rainbowcolor-indigo}{PL-SQL}, \textcolor{rainbowcolor-indigo}{Java 6-8}, \textcolor{rainbowcolor-orange}{Windows 7/10}.}		
      \end{cvitems}
    } 
    
%---------------------------------------------------------
  \cventry
    {Technical Account Manager} % Job title
    {} % Organization
    {} % Location
    {Feb. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities      
		\item[] {\textbf{Context:} Primary technical contact point with one or more clients, assisting in planning, debugging, and supervising ongoing critical business applications.}
		\item[] {\textbf{Functions:} provide technical support for customers to support pre-sales and post-sales processes, address all product-related queries on time, create learning materials and train customers to use products effectively, assist in the creation of support documentation for existing software/service products, provide developers with customer's feedback to help identify potential new features or products, report on product performance, identify solutions to reduce support costs, analyze customer's needs and suggest upgrades or additional features to meet their requirements.}		
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Azure DevOps}, \textcolor{rainbowcolor-green}{TFS}, \textcolor{rainbowcolor-green}{IIS 6-8}, \textcolor{rainbowcolor-green}{VNC}, \textcolor{rainbowcolor-green}{mRemote}, \textcolor{rainbowcolor-green}{Cisco AnyConnect}, %Cisco VPN client, 
\textcolor{rainbowcolor-green}{FortiClient}, \textcolor{rainbowcolor-green}{Teamviewer}, \textcolor{rainbowcolor-green}{Skype/Skype for Business}, \textcolor{rainbowcolor-green}{WebEx}, \textcolor{rainbowcolor-green}{MS Office Suite}, \textcolor{rainbowcolor-green}{Postman}, \textcolor{rainbowcolor-green}{SoapUI},\textcolor{rainbowcolor-green}{Zendesk}, \textcolor{rainbowcolor-green}{Internet Explorer}, \textcolor{rainbowcolor-green}{PowerBI}, \textcolor{rainbowcolor-green}{SSRS/SSIS/SSAS}, \textcolor{rainbowcolor-green}{MS SQL-server 2012-2017},  \textcolor{rainbowcolor-indigo}{T-SQL}, \textcolor{rainbowcolor-orange}{Windows 7}.}		
      \end{cvitems}
    } 
    
%---------------------------------------------------------
  \cventry
    {Software Consultant} % Job title
    {\href{https://www.reditpro.com/}{RedIT} \textbf{(Professional)}} % Organization
    {Lisbon, Portugal} % Location
    {Oct. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities      
		\item[] {\textbf{Context:} 
Adaptive software development and integration with Model-Based architecture for an energy sector company %(cannot disclose from which due to confidentiality agreement terms)
.}
		\item[] {\textbf{Functions:} Integration of Uber-like functionalities into existing Model-Based architecture modules. PL-SQL database replication. Integration, algorithm development, and prototyping of route calculation and schedule assigning software into existing Model-Based architecture modules.}		
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Slack}, \textcolor{rainbowcolor-green}{Git}, \textcolor{rainbowcolor-green}{Visual Studio 2017}, \textcolor{rainbowcolor-green}{MS SQL-server 2016}, \textcolor{rainbowcolor-green}{Oracle SQL developer}, \textcolor{rainbowcolor-indigo}{C\#}, \textcolor{rainbowcolor-indigo}{T-SQL}, \textcolor{rainbowcolor-indigo}{PL-SQL}, \textcolor{rainbowcolor-indigo}{JavaScript}, \textcolor{rainbowcolor-orange}{Windows 7}.}
      \end{cvitems}
    } 
    
%---------------------------------------------------------
  \cventry
    {Software Consultant} % Job title
    {} % Organization
    {} % Location
    {Aug. 2017 - Sept. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities      
%        \item[] {Assistance in the integration of a login functionality managed by Azure AD within a vacation management online solution.}
%%        \item[] {Development and support of an information management system in the areas of social action and health. %used by a Portuguese collective entity of private law and administrative public utility.} 
%        \item[] {Development and bug suTFS, Account Management, teacherpport for an in use information management system in the areas of social action and health. %used by a Portuguese collective entity of private law and administrative public utility.} 
%        \linebreak (\textbf{cannot disclose from which due to confidentiality agreement terms}).}		
		\item[] {\textbf{Context:} 
Adaptive, perfective and corrective software maintenance for an information management system used in the areas of social action and health %(cannot disclose from which due to confidentiality agreement terms)
, lets refer to it as X.}
		\item[] {\textbf{Functions:} Extension and maintenance of all Model-View-Controller (MVC) functionalities, including models, views, controllers, and SQL scripts to update and include new functionalities on X database. Functional and aesthetic bug resolution in views, controllers, and models of X.}		
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{TFS}, \textcolor{rainbowcolor-green}{MS SQL-server 2014}, \textcolor{rainbowcolor-green}{Visual Studio 2013}, \textcolor{rainbowcolor-indigo}{JSP/jQuery/Ajax/JSON/Bootstrap}, \textcolor{rainbowcolor-indigo}{C\#}, \textcolor{rainbowcolor-orange}{Windows 7}.}
      \end{cvitems}
    } 
    
%---------------------------------------------------------
  \cventry
    {Software Consultant} % Job title
    {} % Organization
    {} % Location
    {July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities  
		\item[] {\textbf{Context:} Perfective and corrective software maintenance in the integration of a login functionality managed by Azure AD within a near release vacation management online solution, lets refer to it as Y.}
		\item[] {\textbf{Functions:} Study of Azure AD usage scenarios. Assessment on how to integrate (at the time) Y login process with Azure AD.}		
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Azure AD}, \textcolor{rainbowcolor-green}{Git},  \textcolor{rainbowcolor-green}{MS SQL-server 2016}, \textcolor{rainbowcolor-green}{Visual Studio 2017}, \textcolor{rainbowcolor-green}{Visual Studio Code}, \textcolor{rainbowcolor-indigo}{Angular2/4}, \textcolor{rainbowcolor-indigo}{JSP/jQuery/Ajax/JSON/Bootstrap}, \textcolor{rainbowcolor-indigo}{Node.js}, \textcolor{rainbowcolor-indigo}{C\#}, \textcolor{rainbowcolor-orange}{Windows 7}.}
      \end{cvitems}
    }   

%%---------------------------------------------------------
%  \cventry
%    {PhD Researcher for <\href{http://www.fct.pt/index.phtml.en}{Foundation for Science and Technology}>} % Job title
%    {\href{http://www.it.ubi.pt/medialab}{Instituto de Telecomunica\c{c}\~{o}es and Graphics \& Media Laboratory}} % Organization
%    {Covilh\~a, Portugal} % Location
%    {Jan. 2012 - Present} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%      %\item[] {Engineering and design of a novel modular game engine architecture.}
%      \item[] {Implementation and development of novel pathfinders reactive to influence maps.}%a novel pathfinder and of two novel motion planning algorithms, that integrate influence maps with pathfinders.}
%      %\item[] {Conducting research and case studies on leading edge algorithms and technologies. Writing scientific papers.}
%      %\item[] {Lecturing about achieved results and possible new research trends.}
%      \item[] {Conducting research, writing scientific papers, and lecturing about achieved results and possible new research trends.}
%%        \item[] {Conducting research and case studies on leading edge algorithms and technologies. Writing scientific papers.}
%%        \item[] {Engineering and design of modular game engines.}
%%        \item[] {Implementation and development of innovative motion planning techniques.}
%%        \item[] {Lecturing about achieved results and possible new research trends.}
%%        \item[] {}
%%        \item[] {\textbf{Notable Accomplishments:}}      
%%        \item[] {Proposal of a novel modular game engine architecture.}
%%        \item[] {Proposal of two novel motion planning algorithms, that integrate influence maps with pathfinders.}
%%        \item[] {Proposal of a novel pathfinder.}
%      \end{cvitems}
%    }  
    
%---------------------------------------------------------
  \cventry
    {Research Associate for <PTDC/EIA/70830/2006, \href{http://www.di.ubi.pt/~agomes/moggy/index.html}{MOGGY - A Browser-Based Massive Multiplayer Online Game Engine Architecture}> Project} % Job title
    {\href{http://www.it.ubi.pt/medialab}{Instituto de Telecomunica\c{c}\~{o}es and Graphics \& Media Laboratory} \textbf{(Academic)}} % Organization
    {} % Location
    {Mar. 2008 - Dec. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%		%\item[] {Implementation of a game engine to test state management processing, storage and communication techniques.}        
%		\item[] {Engineering and design of a novel modular game engine architecture to test state management techniques.}
%        \item[] {Implementation of Grid-based solutions to transform multi-player games into MMOGs.}
%        %\item[] {Conducting research and review the state of art regarding Massive Multiplayer Online Games (MMOGs).}		
		\item[] {\textbf{Context:} Study and ultimately attempt to Develop a game engine for MMOGs to work on the browser.}
		\item[] {\textbf{Functions:} Develop a Java game engine prototype, to test state management algorithms. Assist in porting an existing multi-player game (Jake2) to a MMOFPS resorting to GridGain. Implement fluid simulators in the GPU. Elaboration and public presentation of scientific conference articles.}
		\item[] {\textbf{Technologies:} %TexMaker, JabRef,
\textcolor{rainbowcolor-indigo}{GridGain}, \textcolor{rainbowcolor-indigo}{Jgroups}, \textcolor{rainbowcolor-indigo}{JogAmp}, \textcolor{rainbowcolor-indigo}{Apache Math Commons}, \textcolor{rainbowcolor-indigo}{OpenGL}, \textcolor{rainbowcolor-indigo}{CUDA/OpenMP/OpenCL/MPI}
\textcolor{rainbowcolor-indigo}{Java 1.6}, \textcolor{rainbowcolor-indigo}{C/C++}, \textcolor{rainbowcolor-indigo}{LaTeX}, %\textcolor{rainbowcolor-indigo}{Beamer}, 
\textcolor{rainbowcolor-orange}{Windows XP-7}.}
      \end{cvitems}
    }     
    
%---------------------------------------------------------
  \cventry
    {Lab Instructor for the
        11498-Computer Science and Engineering \& \linebreak
		11156-Game Design and Development: 
		\href{http://www.di.ubi.pt/~agomes/tjv/}{Video Games Technologies}	Course 
		\linebreak and the
		5385-Computer Science and Engineering: 		
		\href{http://www.di.ubi.pt/~agomes/cg/}{Computer graphics} Course} % Job title
%    {Lab Instructor for the 
%        \href{http://www.di.ubi.pt/~agomes/tjv/}
%        {Video Games Technologies} course} % Job title
    {\href{http://www.ubi.pt}{Universidade da Beira Interior} \textbf{(Academic)}} % Organization
    {Covilh\~a, Portugal} % Location
    {\linebreak Jan. 2012 - July 2016 \linebreak Jan. 2012 - July 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%		\item[] {Develop laboratory course material, including practical sheets and tests (available upon request).}
%        %\item[] {Responsible for 0.5~hour lecture and supervision of 1.5~hour laboratory.} 
%        %\item[] {Participated in practical project joint assessment with course supervisor.}
%        \item[] {Responsible for 0.5~hour lecture and supervision of 1.5~hour laboratory, and practical project joint assessment.}% with course supervisor	.}		
		\item[] {\textbf{Context:} Lab. assistant in practical component of the video game technologies and computer graphics courses.}
		\item[] {\textbf{Functions:} Develop lab. course material, including practical sheets and tests (available upon request). Responsible for 0.5 hour lecture and supervision of 1.5 hour lab. Participated in practical project joint assessment with course supervisor.}
		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Whiteboard}, \textcolor{rainbowcolor-green}{LibreOffce}, \textcolor{rainbowcolor-green}{JmonkeyEngine}, \textcolor{rainbowcolor-green}{NetBeans}, \textcolor{rainbowcolor-indigo}{Java 1.6-1.8}, \textcolor{rainbowcolor-indigo}{LaTeX}, %\textcolor{rainbowcolor-indigo}{Beamer}, %TexMaker, JabRef,
\textcolor{rainbowcolor-orange}{Windows XP-7}.}
      \end{cvitems}
    }       
    
%---------------------------------------------------------
%  \cventry
%    {Lab Instructor for the
%        11498-Computer Science and Engineering \& \linebreak
%		11156-Game Design and Development: \href{http://www.di.ubi.pt/~agomes/tjv/}
%		{Video Games Technologies} Course} % Job title
%%    {Lab Instructor for the 
%%        \href{http://www.di.ubi.pt/~agomes/tjv/}
%%        {Video Games Technologies} course} % Job title
%    {\href{http://www.ubi.pt}{Universidade da Beira Interior}} % Organization
%    {Covilh\~a, Portugal} % Location
%    {Jan. 2012 - July 2016} % Date(s)
%    {
%%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item[] {Responsible for 0.5~hour lecture and supervision of
%%                1.5~hour laboratory.} %where graduate students learn 
%%                %technologies, techniques, algorithms, data structures, 
%%                %and mathematics behind the design and development of game engines, 
%%                %instead of games themselves.}           
%%        \item[] {Participated in practical project joint assessment 
%%				with course supervisor.}
%%		\item[] {Develop laboratory course material, 
%%                including practical sheets and tests available upon request.}
%%      \end{cvitems}	   
%    }
%    
%%---------------------------------------------------------  
%  \cventry
%    {Lab Instructor for the 5385-Computer Science and Engineering:
%     \href{http://www.di.ubi.pt/~agomes/cg/}{Computer graphics} Course} % Job title
%%    {Lab Instructor for the \href{http://www.di.ubi.pt/~agomes/cg/}{Computer graphics} course} % Job title
%    {} % Organization
%    {} % Location
%    {Jan. 2012 - July 2012} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item[] {Responsible for 0.5~hour lecture and supervision of 
%        		1.5~hour laboratory.} %where undergraduate students are introduced 
%                %2D and 3D computer graphics 
%                %trough GLUT/OpenGL interactive applications programming.}
%        \item[] {Participated in practical project joint assessment 
%				with course supervisor.}		
%      \end{cvitems}
%    }   
    
%---------------------------------------------------------    
  \cventry    
    {Research Associate for <POCI/V/04.01302/0155/0002/2006, "Metodologias Din\^amicas para o Sucesso em Matem\'atica> Project} % Job title
    {} % Organization
    {} % Location
    {July 2007 - Apr. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item[] {Creation of dynamic contents (presentations and work sheets) for theoretical and laboratory mathematics courses.}
%        \item[] {Integration of dynamic content with a content management system (CMS), assessment and extension of CMSs.}
		%\item[] {Research, implementation, and testing of novel modern ways to divulge a math department.}
		\item[] {\textbf{Context:} Develop dynamic ways to dynamize a math department and math teaching at an university level.}
		\item[] {\textbf{Functions:} Creation of dynamic contents (presentations and work sheets) for theoretical and laboratory mathematics courses, i.e., dynamic presentations intended to make math learning more interactive and available outside the class room.}
  		\item[] {\textbf{Technologies:} \textcolor{rainbowcolor-green}{Blackboard}, \textcolor{rainbowcolor-green}{Mathematica}, \textcolor{rainbowcolor-green}{Matlab}, \textcolor{rainbowcolor-green}{LaTeX}, \textcolor{rainbowcolor-green}{Beamer}, %\textcolor{rainbowcolor-green}{TexMaker}, 
  		\textcolor{rainbowcolor-orange}{Windows XP}.}
      \end{cvitems}
    }  
     
%---------------------------------------------------------   
\end{cventries}

\vspace{2.0cm}
