%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}
\usepackage{footmisc}
\renewcommand*{\footnotelayout}{\bodyfontlight\slshape\color{gray}}


% Configure page margins with geometry
\geometry{left=2cm, top=2cm, right=2cm, bottom=2cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
%\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
%\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------

\name{Orlando}{ Pereira}
\address{Dombresson, Switzerland~~-~~Nationality: Portuguese}
\mobile{(+351) 965 038 659} 
\email{orepereira@gmail.com}
\linkedin{orepereira}
\skype{orepereira}



\quote{``If you can't explain it simply, you don't understand it well enough."\\Albert Einstein}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Justine-Hazel Stäuble}
  {experis.ch}
  %{Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}

% The title of the letter
\lettertitle{Job Application for Technical Software Team Leader (J356923AJSB-181116)}
%\lettertitle{Job Application for Software Engineer}

% How the letter is opened
%\letteropening{Dear Mr./Ms./Dr. LastName,}
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Orlando Pereira~~~-~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%\cvsection{About Me}
%\cvsection{Why Google?}
%As a Project Manager at my previous jobs 

Through a leadership position at my previous jobs
(\href{http://edgeinnovation.eu}{Edge Innovation} and \href{http://www.enear.co}{E.Near, Nearshore Technology Solutions}),
I had accountability for the design, implementation, and execution of multi-thousands euros turnkey projects.
Specifically, I had to supervise the entire technical and technological components of all projects.


During that time, I successfully led more than 5 parallel projects through all development phases from initial 
conception through completion within targeted cost, schedule, and goals.
In addition to managing and supervising teams, I also had to participate in the actual development process as an active developer.
In short, I have proven organizational leadership and decision-making skills that can make an immediate contribution to your operations and business development.


%\cvsection{Why Me?}

Some of the qualities and credentials I have to offer are:
\begin{itemize}
	\item MSc, and PhD\footnote{Waiting for the public defense.} in Computer Science and Engineering.
	\item 10+ years of professional experience, including 2 in project management and simultaneously in team-leadership, plus 6+ as a full stack developer.
	\item Expertise in several programming languages, more relevantly, Java (J2EE and J2ME), Objective-C, C, C++, C\#, Swift, and Python.
	\item In-depth knowledge of distributed, parallel, and cloud computational systems, including its communication formats and standards (XML, JSON, SOAP, REST, etc).
	\item Team-focused leader and motivator.	
	\item Expertise in several multidisciplinary technologies (iOS, Android, Unity, Java Swing).
	\item Creative and proactive troubleshooter and problem solver.
\end{itemize}



% final words
Please find my résumé attached. 
An interview would allow me to provide more information about myself and how we could mutually benefit each other.
I am available by phone, email, or skype.
Thank you very much in advance for your consideration, I look forward to hearing from you soon.
%An interview would allow me to provide more information about myself, my multidisciplinary knowledge and explain in detail how we could mutually benefit each other.
%  “Your opening will allow me to combine my interests in wireless networking and embedded security, and I am confident that I can facilitate major upgrades while maintaining the highest levels of security of your WiTrack product.”


\end{cvletter}



%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}